Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-18 arxiv/template.tex
u2 and u3

for $w\gg 1$.  We can use this as a coordinate on the same footing as
circumferential radius $r$.  The first thing to do would be to
suppress $\theta,\phi$ coordinates and consider only $r,t$; see
Figures~\ref{schwarzschild} and~\ref{eddington}.

@@

@@

>>>>

for $w\gg 1$.

\subsection{Equal areas}

We might be interested in preserving areas.  In this case we would use
a coordinate $u_2$, defined by

\begin{equation}
  \frac{u_2^2}{2}=\int\frac{r\,dr}{\sqrt{1-1/r}}
\end{equation}

giving $u_2=\sqrt{I-K}$ where $K$ is a constant of integration and

\begin{equation}
    I = r^2\sqrt{1-{1}/{r}}\left(1+\frac{3}{2r}\right)
 + \frac{3}{8}\log\left(\frac{\sqrt{r}+\sqrt{r-1}}{\sqrt{r}-\sqrt{r-1}}\right)
\end{equation}

Similarly for volume, $u_3=(I-K)^{1/3}$ with

\begin{equation}
    I = r^3\sqrt{1-{1}/{r}}\left(1+\frac{5}{4r} + \frac{15}{8r^2}\right)
+ \frac{5}{16}\log\left(\frac{\sqrt{r}+\sqrt{r-1}}{\sqrt{r}-\sqrt{r-1}}\right)
\end{equation}
\section{Results}

We can use $u_1$ as a coordinate on the same footing as
circumferential radius $r$.  First we suppress $\theta,\phi$
coordinates and consider only $r,t$; see Figures~\ref{schwarzschild},
\ref{eddington}, and ~\ref{gullstrand}.

@@

It is also possible to plot null geodesics for light in an equatorial
plane: figures~\ref{light_2} and \ref{light_closest_2}.  Light
inextensible string is plotted, again for the equatorial case, in
figures~\ref{closest_approach_nonself} and
\ref{closest_approach_self}, for the nonself-intersecting and self
intersecting cases respectively.

@@

\section{Conclusions}
